What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-03 thesis/proposal_draft.Rmd
wednesday update 3

---
title: "Draft Proposal"
author: "Gavin Chin"
output:
  pdf_document: default
  html_document: default
---

@@

```
\begin{center}
Figure 4:  Estimated hourly counts at Flagstaff Station by Day using `geom_smooth()`
\end{center}

@@

@@

  The first step in performing the analysis is to clean the data. In particular, we need to impute the missing values at certain sensor locations. This is cause by two primary reasons: 1) new sensors being installed over time, and 2) sensors not operational for periods of time. A possible model which has been proposed is a GLM (generalized linear model) to estimate a Poisson regression: $$\text{HourlyCounts} \sim \text{Year} \times \text{HDay} \times \text{Time} + \text{Month} \label{poisson_model} \tag{1}$$

>>>>

---
title: "What can we learn about life in the city by mining the Melbourne’s Open Data Platform?"
subtitle: "Thesis Proposal"
date: April 2017
author: 
- "Gavin Chin"
- "supervised by Dianne Cook"
output:
  pdf_document: default
  html_document: default
---

@@

```
\begin{center}
Figure 4:  Estimated hourly counts at Flagstaff Station by Day 
\end{center}

@@

#### R and Shiny Apps

R is an open source programming language used for statistical computing.

@@

  The first step in performing the analysis is to clean the data. In particular, we need to impute the missing values at certain sensor locations. This is cause by two primary reasons: 1) new sensors being installed over time, and 2) sensors not operational for periods of time. A possible model which has been proposed is a GLM (generalized linear model) to estimate a Poisson regression: 
\begin{align*}
\text{HourlyCounts} & \sim\text{Year}\times\text{HDay}\times\text{Time}+\text{Month}\tag{1}\\
\Rightarrow\qquad\lambda_{i} & =\beta_{0}+\beta_{1}\text{Year}\times\text{HDay}\times\text{Time}+\beta_{2}\text{Month}\\
\text{HourlyCounts}_{i} & =\text{Poisson}\left(\lambda_{i}\right)
\end{align*}
